Generative Adversarial Networks

### 2017-12-05 cs6735/assignment/report.tex
start assignment report

@@

\subsection{ID3}
\subsection{Naïve Bayes}
\subsection{Adaboost}
\subsection{Random Forest}
\subsection{K-Nearest Neighbors}

>>>>

\section{Objectives}
\begin{enumerate}
  \item Implement the following machine learning algorithms:
  \begin{enumerate}
    \item ID3
    \item Adaboost on ID3
    \item Random Forest
    \item Naïve Bayes
    \item Adaboost on Naïve Bayes
    \item K-nearest neighbors
  \end{enumerate}
  \item Evaluate the algorithms on the following datasets:
  \begin{enumerate}
    \item Brest Cancer Data
    \item Car Data
    \item Ecoli Data
    \item Mushroom Data
  \end{enumerate}
  \item Create report of the experimental study including:
  \begin{enumerate}
    \item Description of the learning algorithms you implement.
    \item Description of the datasets you use (number of examples, number of attribute, number of classes, type of attributes, etc.).
    \item Technical details of your implementation: pre-processing of data sets (discretization, etc.), parameter setting, etc.
    \item Design of your programming implementation (data structures, overall program structure).
    \item Report and analysis of your experimental results using using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
    \item Comparison and discussion of the algorithms with respect to the experimental results.
  \end{enumerate}
\end{enumerate}

@@

\subsection{ID3}
The Iterative Dichotomiser 3 (ID3) algorithm is a decision tree algorithm used to efficiently develop decision trees \cite{Quinlan:1986:IDT:637962.637969}. This algorithm was developed for situations where there are large amount of attributes and training sets which contain many attributes, but there was the need to be able to efficiently develop relatively well performing decision trees.

The algorithm begins at the root node with a set of catigorical, labled data $S$.

\subsection{Naïve Bayes}
\subsection{Adaboost}
\subsection{Random Forest}
\subsection{K-Nearest Neighbors}
